### 2016-09-29 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point()+
    stat_smooth(col = 'darkgrey',lty = 3,se = F)+
  stat_smooth(method = 'lm',col='darkgrey',formula = y~log(x),se = F)
  annotate('text',x = 1,y = 2.8,label = 'A')

@@

Fig1B <- ggplot(temp,aes(x = DeltaAge,y = RTL))+
  ylab('RTL') + 
  xlab(expression(Delta*' age (months)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = -100,y = 2.1,label = 'B')

@@

temp <- subset(juv_r,Season == 'Major')
temp$LogAge <- log(temp$Agemonths)

@@

@@

>>>>

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col = 'darkgrey')+
  stat_smooth(method = 'lm',col='darkblue',fill = 'darkblue',formula = y~log(x),se = T)+
  annotate('text',x = 1,y = 2.9,label = 'A')

@@

Fig1B <- ggplot(temp,aes(x = DeltaAge,y = RTL))+
  ylab('RTL') + 
  xlab(expression(Delta*' age (months)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col = 'darkblue',fill = 'darkblue')+
  annotate('text',x = -100,y = 2.9,label = 'B')

@@

temp <- dd
temp$LogAge <- log(temp$Agemonths+1)

temp2 <- subset(temp,CatchYear<2014)

temp2$cenTL <- (temp2$RTL-tapply(temp2$RTL,temp2$Agemonths,mean)[as.character(temp2$Agemonths)])/tapply(temp2$RTL,temp2$Agemonths,sd)[as.character(temp2$Agemonths)]

#temp2 <- subset(temp2,Whodunnit != 'EAF')
temp2 <- subset(temp2,!is.na(Agemonths))
temp2 <- subset(temp2,Agemonths>10)

temp2$obs <- c(1:nrow(temp2))

summary(glmer(SurvivedNext~RTL+Agemonths+(1|BirdID)+(1|obs),data=temp2,family = 'binomial',control = glmerControl(optimizer = "bobyqa")))
summary(glm(SurvivedNext~RTL+Agemonths,data=temp2,family = 'binomial'))

ggplot(temp2,aes(y = RTL,x = Agemonths,col = factor(SurvivedNext)))+
  geom_point()+
  stat_smooth()
x <- tapply(temp2$RTL,list(temp2$SurvivedNext,factor(temp2$Agemonths)),mean)[,1:10]
plot(x[1,],type = 'l')
points(x[2,],type = 'l',lty = 2)

@@

summary(lm2)
confint.merMod(lm2)

@@

```{r Figure X}

temp <- dd
#temp$SurvivedNext <- factor(temp$SurvivedNext)
temp$SN2 <- with(temp,paste(Sex,SurvivedNext))

FigX <- ggplot(temp,aes(x = LayYear,y = RTL,col = SN2))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_point()+
  stat_smooth()

FigX

FigX <- ggplot(subset(temp,Agemonths),aes(x = SN2,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_boxplot()

FigX
